Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds

### 2016-02-01 paper.tex
updating figures

Our kinematic prescription for a biconical disc wind model
follows \cite{SV93}, and is described further by
LK02, H13 and M15. {\bf We emphasise that the purpose of this
purely kinematic wind model is to provide a simple tool for 
exploring different outflow geometries and kinematics, and
the model itself is not hydrodynamic.}
A schematic is shown in Fig.~\ref{fig:cartoon},
with key aspects marked. The general biconical
geometry is similar to that invoked by \cite{MCGV95} and 
\cite{elvis2000} to explain the phenomenonology
of quasars and BALQSOs. {\bf However, we do not include the initial
vertical component present in the Elvis (2000) model, which was
invoked as a qualitative explanation for narrow absorption lines}.

>>>>

Our kinematic prescription for a biconical disc wind model
follows \cite{SV93}, and is described further by
LK02, H13 and M15. {\bf We emphasise that the purpose of this
purely kinematic wind model is to provide a simple tool for 
exploring different outflow geometries and kinematics.}
A schematic is shown in Fig.~\ref{fig:cartoon},
with key aspects marked. The general biconical
geometry is similar to that invoked by \cite{MCGV95} and 
\cite{elvis2000} to explain the phenomenonology
of quasars and BALQSOs. {\bf However, we do not include the initial
vertical component present in the Elvis (2000) model, which was
invoked as a qualitative explanation for narrow absorption lines}.
